MonteCarlo Simulation's of the Covid-19 Pandemic

### 2022-12-14 paper.rmd
updatepaper

# Introduction (Should we do an Abstract?)

@@

*Insert text here*

# Chien: Italy

>>>>

# Introduction

@@

## Available Official Data (Positive Cases)

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold", out.width="50%"}
# extract China data of interest
china <- data |>
  filter(location == "China") |>
  filter(date >= "2020-01-22", date <= "2020-03-28") |>
  select(c(date, total_cases, total_deaths)) |>
  mutate(days = 1:n())

# recreate plots
positive <- ggplot(data = china) +
  geom_point(aes(x = date, y = total_cases)) +
  theme(title =element_text(size=6)) +
  labs(x = "Date", y = "China cumulative number of cases")
positive
```

## Available Official Data (Fatalities)

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold", out.width="50%"}
ggplot(data = china) +
  geom_point(aes(x = date, y = total_deaths)) +
  theme(title =element_text(size=6)) +
  labs(x = "Date", y = "China cumulative number of fatalities") +
  ylim(0,5000)
```

## Fit by the Gauss Error Function

Apply an $nls$ function to determine the nonlinear (weighted) least-squares estimates of the four parameters $a,b,c,d$ of a Gauss error function model: $a+b*erf(c*x-d)$.

```{r, include=FALSE, message=FALSE, warning=FALSE}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
```

```{r, message=FALSE, warning=FALSE}
model <- nls(total_cases ~ gauss_fn(days,a,b,c,d), 
             data=china, 
             start=list(a=10000,b=10000,c=0.1,d=1))
```

## Fit by the Gauss Error Function and Peak Day (Positive Cases)

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
try <- china$total_cases
model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=2200,b=2200,c=0.1,d=1))
est_try <- summary(model_try)$parameters
est_try <- est_try[, 1]
names(est_try) <- NULL
fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}

# find the second derivative of fitted function
# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
fn_try_deriv <- D(fn_try_deriv,'x')
x=seq(1,67,length.out=6700)
tmp <- eval(fn_try_deriv)
peak1 <- min(x[tmp < 0])
```

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
# summary(model1)$parameters
fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_cases)) +
  theme(title =element_text(size=6)) +
  labs(x = "Days", y = "China cumulative number of cases") +
  stat_function(fun=fn_model1, color="#d33636", size=1.5) +
  geom_vline(xintercept = peak1, color="#d33636", size=1.5, linetype="dashed")
```

## Fit by the Gauss Error Function and Peak Day (Fatalities)

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
try <- china$total_deaths
model_try <- nls(try ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=2200,b=2200,c=0.1,d=1))
est_try <- summary(model_try)$parameters
est_try <- est_try[, 1]
names(est_try) <- NULL
fn_try <- function(x, ests) {ests[1]  + ests[2] * erf(ests[3] * x - ests[4])}

# find the second derivative of fitted function
# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
fn_try_deriv <- D(fn_try_deriv,'x')
x=seq(1,67,length.out=6700)
tmp <- eval(fn_try_deriv)
peak2 <- min(x[tmp < 0])
```

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths)) +
  theme(title =element_text(size=6)) +
  labs(x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2, color="#1b95ff", size=1.5) +
  geom_vline(xintercept = peak2, color="#1b95ff", size=1.5, linetype="dashed")
```

# Italy
